### 2020-06-11 chapters/sota.tex
Document structure

\subsubsection*{Time complexity analysis}

@@

\subsubsection*{Space complexity analysis}
Extra-N has to keep a lifetime neighbor count dictionary-like object for each window data point. For that reason, we claim that Extra-N achieves linear memory consumption relative to the number of data points in the window.

@@

\subsection{Real-Time Stream Anomaly Detection with Hierarchical Temporal Memory}
HTM
\iffalse
HTM\\
point outlier, model-based, prediction\\
black-box ML algorithm\\
explain properties\\
use what authors say in their review\\
\fi
\subsection{DeepAnT}
DeepAnT
\iffalse
DeepAnT\\
point outlier, model-based, prediction\\
black box DL algorithm\\
explain properties\\
use what authors say in their review\\
\fi

@@

\subsection{A two window paradigm algorithm for change detection}

>>>>

\subsubsection*{Method classification}
Extra-N can take both uni or multivariate time-series as input data. However, it does not relate multiple time-series and does not take into account possible dependencies between different time-dependent variables. In that sense, and according to the presented taxonomy (Figure \ref{fig:outlier-taxonomy}), the method is of univariate nature. Last but not least, Extra-N aims to detect univariate point outliers. These point outliers are identified based on the density of the region or neighborhood they belong too. Hence, we say Extra-N is a density-based method (Figure \ref{fig:point-outlier-taxonomy}).

\subsubsection*{Time complexity}

@@

\subsubsection*{Space complexity}
Extra-N has to keep a lifetime neighbor count dictionary-like object for each window data point. For that reason, we claim that Extra-N achieves linear memory consumption relative to the number of data points in the window.

@@

\subsection{Real-Time Stream Anomaly Detection with Hierarchical Temporal Memory}
\subsubsection*{Method classification}
\subsubsection*{Applicability to our Hypothesis}

\iffalse
HTM\\
point outlier, model-based, prediction\\
black-box ML algorithm\\
explain properties\\
use what authors say in their review\\
\fi
\subsection{DeepAnT}
\subsubsection*{Method classification}
\subsubsection*{Applicability to our Hypothesis}

\iffalse
DeepAnT\\
point outlier, model-based, prediction\\
black box DL algorithm\\
explain properties\\
use what authors say in their review\\
\fi

@@

\subsection{A two window paradigm algorithm for change detection}
\subsubsection*{Method classification}
\subsubsection*{Time complexity}
\subsubsection*{Space complexity}
\subsubsection*{Applicability to our Hypothesis}
